---
title: "CAS datascience script"
author: "Oliver Speer"
date: 6.9.2023
format: html
editor: visual
---

## ZHAW web-Umgebung

Lerninhalte an der ZHAW werden in moodle <https://moodle.zhaw.ch/enrol/index.php?id=15611> bereitgestellt. Zugangs-Management via edu-ID <https://login.eduid.ch/idp/profile/SAML2/Redirect/SSO?execution=e1s4>.

Zugangsadmin für ZHAW Umgebung: <https://selfservice.zhaw.ch/index.html>.

## Installation R und RStudio

<https://moodle.zhaw.ch/pluginfile.php/1344143/mod_resource/content/3/Einstieg_in_R_und_RStudio.pdf>

## Kursdaten

<https://moodle.zhaw.ch/pluginfile.php/1344144/mod_resource/content/3/CAS-DA2023-18_Kursdaten_HS.pdf>

## Modul A - Statistische Grundlagen der Datenanalyse


## Modul B - Multiple Regression, die Basis der Datenanalyse und Prognose

## Modul C - Data Mining mit Schwerpunkt Clustering und Klassifikation



When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
